---
output: github_document
---

<!---
  Licensed to the Apache Software Foundation (ASF) under one
  or more contributor license agreements.  See the NOTICE file
  distributed with this work for additional information
  regarding copyright ownership.  The ASF licenses this file
  to you under the Apache License, Version 2.0 (the
  "License"); you may not use this file except in compliance
  with the License.  You may obtain a copy of the License at
    http://www.apache.org/licenses/LICENSE-2.0
  Unless required by applicable law or agreed to in writing,
  software distributed under the License is distributed on an
  "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
  KIND, either express or implied.  See the License for the
  specific language governing permissions and limitations
  under the License.
-->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# adbcdrivermanager

<!-- badges: start -->
<!-- badges: end -->

The goal of adbcdrivermanager is to provide a low-level developer-facing interface
to Arrow Database Connectivity (ADBC) for the purposes of driver development, testing,
and support for user-facing packages that rely on ADBC drivers.

## Installation

You can install the development version of adbcdrivermanager from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("apache/arrow-adbc/r/adbcdrivermanager")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(adbcdrivermanager)

# Get a reference to a database using a driver. The adbcdrivermanager package
# contains a few drivers useful for illustration and testing.
db <- adbc_database_init(adbc_driver_monkey())

# Open a new connection to a database
con <- adbc_connection_init(db)

# Initialize a new statement from a connection
stmt <- adbc_statement_init(con)

# The monkey driver allows you to specify the data for a query
# in advance for testing purposes
adbc_statement_bind_stream(stmt, nycflights13::flights)

# Set the query
adbc_statement_set_sql_query(stmt, "SELECT * FROM flights")

# Start executing the query. Results in ADBC are ArrowArrayStream objects,
# which can be materialized using as.data.frame(), as_tibble(),
# or converted to an arrow::RecordBatchReader using
# arrow::as_record_batch_reader()
stream <- nanoarrow::nanoarrow_allocate_array_stream()
adbc_statement_execute_query(stmt, stream)

# Materialize the whole query as a tibble
tibble::as_tibble(stream)

# Clean up!
adbc_statement_release(stmt)
adbc_connection_release(con)
adbc_database_release(db)
```
